---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{r}
library(tidyverse)
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vR_yFVNX242un9XFR7YuglMjHCQqkEN3Lkqq6jFFdEpScQ375cJUllypfWKOuemBQWP2IPq7hauoWYw/pub?gid=905058073&single=true&output=csv")

latest_data <- logged_data %>%
  select(Timestamp,
         category = 'What category best describes this Instagram advertisement?',
         format = 'What format was the advertisement in?',
         panels = 'How many panels / screens were shown in the advertisement?',
         time = 'When was this advertisement observed?',
         relevant = 'Was this advertisement relevant to you?')
```

```{css}

```
## Instagram advertisement patterns

This section explores how advertisement categories vary between day and night.


```{r}
ggplot(latest_data, aes(x= category, fill = time)) + geom_bar(position = "dodge") + labs (title = "Advertisement category by time of day", x= "Category", y= "Count", fill = "Time of day") + theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, hjust = 1))

```



This section explores which advertisement formats (image, video, carousel) are most commonly used within each category.


```{r}
ggplot(latest_data, aes(x= category, fill = format)) + geom_bar(position = "dodge") + labs(title = "Advertisement format across categories", x= "category", y= "Count", fill= "Format") + theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
top_category <- names(sort(table(latest_data$category), decreasing = TRUE))[1]
top_format <- names(sort(table(latest_data$format), decreasing = TRUE))[1]
```
The most common advertisement category in this dataset is `r top_category`, and the most frequently used advertisement format is `r top_format`. This suggests that visually driven content is pariculary dominant in this category.

