---
title: "Project4_report"
author: "Lora Joo"
date: "2026-05-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This project focused on analysing patterns in Instagram advertisements observed during daily social media use. I continued using the Google Form created in Project 2 to record variables such as advertisement category, advertisement format (image, video, and carousel), number of panels, time of day, relevance, and timestamp data. I was interested in exploring whether advertisement patterns changed depending on category, format and observation time.

The data was collected over multiple weeks by directly observing advertisements while using Instagram. In particular, I wanted to investigate which advertisement categories appeared most frequently, whether certain advertisement formats were more common within specific categories, and how advertisement observations varied throughout the day. 

For the visualisations, I used grouped bar charts and a line graph. The bar charts were suitable for aomparing frequencies across categories and advertisement formats, while the line graph was useful for showing how advertisement observations changed over time using timestamp data. I also adjusted the colour palette and rotated axis labels to improve readability. Initially, some graphs had overlapping labels and weak colour contrast, but these issues were improved by modifying the graph layout and colour theme.

## Visual data story

This visual data story was designed to explore how Instagram advertisement pattens changed across categories, advertisement formats, and observation times. Rather than displaying graphs individually, the HTML format allowed the visualisations to appear progressively as the user scrolls through the webpage, helping create a clearer narrative flow and more interactive reading experience. 

Different geoms, including grouped bar charts and a line graph, were used to highlight different relationships within the data. The first visualisation compared advertisement categories between day and night, while the second focused on how advertisement formats varied across categories. The final visualisation used timestamp data to show how advertisement observations changed. throughout the day, revealing a noticeable increase during the afternoon period.

Accessibility and readability were also considered throughout the design process. Alternative text was included for all visualisations, while axis label rotation and a consistent colour palette were used to reduce clutter and improve visual consistency. These features helped transform the project from a collection of separate graphs into a more cohesive visual data story. 

## Learning reflection

Through this project, I learned that planning the data collection process carefully before starting is very important. If the variables are not planned properly in advance, it becomes difficult to create meaningful comparisons during the visualisation stage. In particular, it was important to understand how variables such as advertisement category, format, time of day, relevance, and timestamp could relate to each other. 

I also learned that understanding the relationships between variables is more important than simply collecting a large amount of data. While creating the visualisations, I needed to think carefully about which variables could be combined together and which graph types were most suitable for showing those relationships. For example, combining category and time_of_day helped compare advertisement patterns, while timestamp data helped show how observations changed over time.

This project showed me that data visualisation is not only about creating graphs, but also about understanding relationships within the data and communicating those patterns clearly. In future projects, I would like to spend more time planning the overall visual story before beginning the data collection process.

## Appendix 

```{r file ='data_visualisation.R', eval=FALSE, echo=TRUE}

```